Wolbachia, Toxoplasma and O. Cordyceps: Extreme Host-Manipulating Microbes That Changed the World

### 2015-12-16 paper.tex
Fixed referencing issue
added a bit about darwin and the state of science when cordyceps was first discovered

\textit{Ophiocordyceps unilateralis} was first discovered by the British naturalist Alfred Russel Wallace who, probably not coincidently, is best known for independently conceiving the theory of evolution through natural selection.

>>>>

\textit{Ophiocordyceps unilateralis} was first discovered in 1859 by the British naturalist Alfred Russel Wallace who, probably not coincidently, is best known for independently conceiving the theory of evolution through natural selection. Darwin published his now famous "On the Origin of Species" in the same year, which gives some good context as to where the scientific paradigms were at the time.\cite{darwin}
